Microlensing as a possible probe of event-horizon structure in quasars

### 2017-06-27 paper1/ms.tex
editing

In Section~\ref{sec:source-models} we introduce the three source
profiles used in our subsequent models and simulations: a
constant-brightness disc, a circular Gaussian, and the crescent source
introduced by \citep{2013MNRAS.434..765K}.  The latter is simply a
constant-brightness disc with a smaller, non-concentric disc cut out
of it.  We also derive the half-light radius for a crescent.  The
half-light radius can characterise the source size for all three types
of source.

@@

We now proceed to fit the mock lightcurve using MCMC, to recover the
source parameters.

Note that fitting involves three nuisance parameters, namely the
brightness normalisation and the start and end points on the path.
The latter two are equivalent to considering the location of the
caustic with respect to the starting point and the speed of the
source.  The fitting method automatically marginalises over all the
nuisance parameters.

Widely used \citep[e.g.,][]{2010ApJ...712..658P}.

>>>>

In Section~\ref{sec:source-models} we introduce the three source
profiles used in our subsequent models and simulations: a
constant-brightness disc, a circular Gaussian, and the crescent source
introduced by \cite{2013MNRAS.434..765K}.  The latter is simply a
constant-brightness disc with a smaller, non-concentric disc cut out
of it.  We also derive the half-light radius for a crescent.  The
half-light radius can characterise the source size for all three types
of source.

@@

We now proceed to fit the mock lightcurve.  The basic fitting
technique is the same as used in several previous studies
\citep[e.g.,][]{2010ApJ...712..658P}.  Markov-Chain Monte-Carlo is
used to fit source parameters and additional nuisance parameters (see
below) jointly, and then marginalise out all uninteresting parameters,
leaving posterior distributions for any chosen parameter.

In addition to the source parameters, the fitting procedure includes
three nuisance parameters, namely the brightness normalisation and the
start and end points on the path.  The latter two are equivalent to
considering the location of the caustic with respect to the starting
point and the velocity component of the source transverse to the
caustic (that is, $v_{\!\perp}$).  The orientation of the source track
is another nuisance parameter, which we do not include it separately.
This is because, for a pure fold, changing the orientation of the
source track is equivalent to changing $v_{\!\perp}$ and the
orientation of the source (see Figure~\ref{fig:infinite_fold}), all
parameters that are included.  In the present case, the caustic is a
clean but non-ideal fold, hence disregarding the orientation of the
source track is expected to introduce some systematic error.
